A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-12 tex/main.tex
Move some of Marc's notes for further work.
Moving these to the conclusion.
Write introductory paragraph.
Highlighting the differences with a classic Moran process.

          To the authors knowledge this is the largest
          such study. It allows for insights about the behaviour and
          performance of strategies with regard to their survival in an
          evolutionary setting.
          }  % TODO Add main conclusion/finding.

@@

Main questions are:

\begin{enumerate}
    \item What strategies are good invaders?
    \item What strategies are good at resisting invasion?
    \item How do 1 and 2 change as a function of population size?
\end{enumerate}

A key point here is that the relative fitness of a strategy depends on the
population distribution. The original Moran process assumes a relative fitness
of r of one strategy over the other, giving a fixation probability for the
starting population $(i, N-i)$ (when $r != 1$)

>>>>

          To the authors knowledge this is the largest
          such study. It allows for insights about the behaviour and
          performance of strategies with regard to their survival in an
          evolutionary setting.
\end{abstract}  % TODO Add main conclusion/finding.

@@

Since the formulation of the Moran Process in \cite{Moran1957}, this model of
evolutionary population dynamics has been used to gain insights about the
evolutionary stability of strategies in a number of settings. Similarly since
the first Iterated Prisoner's Dilemma (IPD) tournament described in
\cite{Axelrod1980a} the Prisoner's dilemma has been used to understand the
evolution of cooperative behaviour in complex systems.

The analytical models of a Moran process are based on the relative fitness
between two strategies and take this to be a fixed value \(r\) \cite{Nowak}.
This is a valid model for simple strategies of the Prisoner's Dilemma such as to
\textit{always cooperate} or \textit{always defect}. This manuscript provides a
detailed numerical analysis of \textbf{172} complex and adaptive strategies for
the IPD\@. In this case the relative fitness of a strategy is dependent on the
population distribution.

This provides answers to the following questions:

\begin{enumerate}
    \item What strategies are good invaders?
    \item What strategies are good at resisting invasion?
    \item How does the population size affect these findings?
\end{enumerate}
